Results_paper1

### 2019-04-09 Exploring/Detect_MCSs.Rmd
fixed_bits

# OISSTDir <- "~/Documents/Masters_2019/Data_SST"
# OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
#             col.names = c("lon", "lat", "temp", "date"))

OISST <- as.tibble(fread("Data/csvavhrr-only-v2-19810901-20180630.csv"))
# # Quick visualisation of the data
# # To explore the data I visualise the min temperatures along the South african coastline.
# 
# OISST %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
# ggsave(plot = OISST, filename = "Figures/OISST")
```

@@

```{r}
# unique_pixel <- OISST %>%
#   select(lon, lat) %>%
#   unique()
# 
# # Select nearest 1 pixels (k = 1)
# # here we use knnx to find the closes 1 pixels to the insitu sites
# match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
#                           query = as.matrix(combined_US[,5:6]), k = 1)
# 
# # Select SST pixels nearest to insitu sites
# pixel_match <- unique_pixel[match_index,] %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   mutate(site = combined_US$site)
# 
# ## Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
# OISST_match <- OISST %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   filter(combi %in% pixel_match$combi)
# 
# ## Visualisation
# ggplot(data = OISST_match, aes(x = date, y = temp_OISST)) +
#   geom_line() +
#   facet_wrap(~combi)
# ggsave(plot = OISST_match, filename = "Figures/combined_OISST_match")
# 
# OISST_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
```

>>>>

OISSTDir <- "~/Documents/Masters_2019/Data_SST"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))

# OISST <- as.tibble(fread("Data/csvavhrr-only-v2-19810901-20180630.csv"))
# # Quick visualisation of the data
# # To explore the data I visualise the min temperatures along the South african coastline.
# 
# OISST %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
# ggsave(plot = OISST, filename = "Figures/OISST")
```

@@

```{r}
unique_pixel <- OISST %>%
  select(lon, lat) %>%
  unique()
# 
# # Select nearest 1 pixels (k = 1)
# # here we use knnx to find the closes 1 pixels to the insitu sites
match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)
# 
# # Select SST pixels nearest to insitu sites
# pixel_match <- unique_pixel[match_index,] %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   mutate(site = combined_US$site)
# 
# ## Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
# OISST_match <- OISST %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   filter(combi %in% pixel_match$combi)
# 
# ## Visualisation
# ggplot(data = OISST_match, aes(x = date, y = temp_OISST)) +
#   geom_line() +
#   facet_wrap(~combi)
# ggsave(plot = OISST_match, filename = "Figures/combined_OISST_match")
# 
# OISST_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
```

### 2019-04-09 Paper1_results.Rmd
fixed_bits

```{r load_files1, include=TRUE}
load("Data/site_list_v4.2.RData")
load("Data/SACTN_daily_v4.2.RData")
```

@@

```{r}
site_list_sub <- site_list %>%
  filter(coast == "wc") %>%
  filter(length > 3650) 
site_list_sub <- site_list_sub[c(-2, -3, -5, -6, -7,-9, -12, -13, -14),] # Here I keep all the sites with temperature obtained up to 2017
save(site_list_sub, file = "Data_P1/site_list_sub")

@@

In this thesis, different remotely-sensed SST datasets are used. Hence, these datasets represent different resolutions at which data was obtained. We will make use of five remotely-sensed SST datasets, these include; the  MUR, AVHRR OISST, K10 and G1SST data. **MODIS SST data need to be downloaded and used too**

@@

insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()
# save(insitu_MUR, file = "Data_P1/insitu_MUR.RData")

@@

MUR_plot <- match_plot(df = insitu_MUR)

temp_plot <- function(df){
  temp_plot <- df %>% 
  ggplot(aes(x = date, y = temp, colour = site)) +
    geom_line(aes(group = site)) +
    labs(x = "", y = "Temperature (°C)") +
    theme(axis.text.x = element_text(angle = 45)) +
    theme(legend.position = "top")
}
MUR_plot <- temp_plot(df = insitu_MUR)
```

@@

insitu_G1SST <- match_func(df = G1SSTsub_SST) 
save(insitu_G1SST, file = "Data_P1/insitu_G1SST.RData")
G1SST_plot <- match_plot(df = insitu_G1SST )
G1SST_temp_plot <- temp_plot(df = insitu_G1SST)
```

@@

insitu_K10 <- match_func(df = K10_SST) 
# save(insitu_K10, file = "Data_P1/insitu_K10.RData")

K10_plot <- match_plot(df = insitu_K10)
k10_temp_plot <- temp_plot(df = insitu_K10)
```

@@

load("Data_P1/SACTN_overlap.RData") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data

@@

# Select nearest 1 pixels (k = 1)
# Here I use knnx to find the closes 1 pixels to the insitu sites
match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                      query = as.matrix(SACTN_overlap[,5:6]), k = 1)

# Select SST pixels nearest to insitu sites
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = SACTN_overlap$site)
# save(pixel_match, file = "Data_P1/pixel_match.RData")
load("Data_P1/pixel_match.RData")

@@

load("Data_P1/OISST_match.RData")
OISST_sites <- OISST_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) %>%
  dplyr::rename(temp_OISST =temp)

# Visualise time series
ggplot(data = OISST_sites, aes(x = date, y = temp)) +
  geom_line() +
  facet_wrap(~site)

# save(OISST_sites, file = "Data/OISST_sites.RData")
load("~/Documents/Masters_2019/MastersProject/Data/OISST_sites.RData")
OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
```

## Matching the Insitu data with the OISST SST data
```{r}
insitu_OISST <- match_func(df = OISST_sites)
# save(insitu_OISST, file = "Data/insitu_OISST.RData")
OISST_plot <- match_plot(df = insitu_OISST)
OISST_temp_plot <- temp_plot(df = insitu_OISST)
```

>>>>

```{r load_files1, include=TRUE}
load("Data_P1/site_list_v4.2.RData")
load("Data_P1/SACTN_daily_v4.2.RData")
```

@@

```{r}
site_list_sub <- site_list %>%
  filter(coast == "wc") %>%
  filter(length > 3650) 
site_list_sub <- site_list_sub[c(-2, -3, -5, -6, -7,-9, -12, -13, -14),] # Here I keep all the sites with temperature obtained up to 2017
save(site_list_sub, file = "Data_P1/site_list_sub.Rdata")

@@

In this thesis, different remotely-sensed SST datasets are used. Hence, these datasets represent different resolutions at which data was obtained.

@@

@@

temp_plot <- function(df){
  temp_plot <- df %>% 
  ggplot(aes(x = date, y = temp, colour = site)) +
    geom_line(aes(group = site)) +
    labs(x = "", y = "Temperature (°C)") +
    theme(axis.text.x = element_text(angle = 45)) +
    theme(legend.position = "top")
}

## Matching the in-situ data with the G1SST SST data
insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()
# save(insitu_MUR, file = "Data_P1/insitu_MUR.RData")
MUR_plot <- match_plot(df = insitu_MUR)
MUR_plot <- temp_plot(df = insitu_MUR)
```

@@

## Matching the Insitu data with the G1SST SST data
insitu_G1SST <- match_func(df = G1SSTsub_SST) 
# save(insitu_G1SST, file = "Data_P1/insitu_G1SST.RData")
G1SST_plot <- match_plot(df = insitu_G1SST )
G1SST_temp_plot <- temp_plot(df = insitu_G1SST)
```

@@

## Matching the Insitu data with the K10 SST data
insitu_K10 <- match_func(df = K10_SST) 
# save(insitu_K10, file = "Data_P1/insitu_K10.RData")
K10_plot <- match_plot(df = insitu_K10)
k10_temp_plot <- temp_plot(df = insitu_K10)
```

@@

load("Data_P1/site_list_sub.RData") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data

@@

# Select nearest 1 pixels (k = 1)
# Here I use knnx to find the closes 1 pixels to the insitu sites
match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                      query = as.matrix(site_list_sub[,5:6]), k = 1)

pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = site_list_sub$site)

@@

OISST_sites <- OISST_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) %>%
  dplyr::rename(temp_OISST =temp)

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
# save(OISST_sites, file = "Data_P1/OISST_sites.RData")

## Matching the Insitu data with the OISST SST data
insitu_OISST <- match_func(df = OISST_sites)
# save(insitu_OISST, file = "Data_P1/insitu_OISST.RData")
OISST_plot <- match_plot(df = insitu_OISST)
OISST_temp_plot <- temp_plot(df = insitu_OISST)
```
